\LARGE \bf Analysis of the effectiveness of recursive networks in the classification task

### 2019-06-12 paper/main.tex
paper: Conclusions

Based on the qualitative results one can say, that convulutional neural networks achieve better accuracy then ReNet and ReNet with modfication. In 3 out of 4 used datasets modified ReNet obtained similar or better results then ReNet. For Natural Images dataset ReNet outperformes ReNet with modification. For the last dataset some issues were observed and 7 layers of ReNet with modification were need. This shows, that modification introduced in this paper is applicable to all datasets. Introducing modification yielded in substantial speedup for the same datasets, where no performance decrease was noted.

In the tSNE visualization for convolutional network each class forms unified cluster with the exception of few outliers. Based on provided plot one can assume, that each class is easily linearly separable from another. Only mixed classes are 2 and 3. This classes correspond to dog and cat, while other are for example flower, car or airplane. In given situation it is reasonable why cat and dog classes are perceived as similar compared to other classes. The same cannot be found for ReNet networks. Learned representation for both ReNet and ReNet with modification are not linearly separable. There are some Fragments of representation, where one of classes is dominant, but all labels are mixed up. This may be reason why classification task is difficult for ReNet networks.

Assuming that the loss landscape visualization plots are representative one may assume, that ReNet networks have obtained minimum. This minimum can be global or local. If minimum is global, then ReNet networks are not able of achieving minimums with low value that is close to loss obtained by convolutional networks. However results discussed in \cite{Goodfellow-et-al-2016} provide, that deep networks rarely obtain global minimum. Most of the times achived minimum is local, but the value of loss is sufficiently low. One of possibilities is that ReNet networks require some special optimization techniques.

>>>>

Based on the qualitative results we can conclude, that convulutional neural networks achieve a better accuracy then the ReNet and the ReNet with modfication. In 3 out of 4 datasets the modified ReNet obtained similar or better results then the original ReNet. For the Natural Images dataset the ReNet outperformes the ReNet with modification. In case of the last dataset some issues were observed. 7 layers of the ReNet with modification were needed to obtain reported results. This shows, that the modification introduced in this paper is not applicable to all datasets without the accuracy decrease. Introducing modification yielded in substantial speedup for the same datasets, where no performance decrease was noted.

In the tSNE visualization for the convolutional network each class forms an unified cluster with the exception of few outliers. Based on provided plot we can assume, that each class can be easily linearly separated from another. Only mixed classes are 2 and 3. This classes correspond to dog and cat, while other in this dataset are flower, car or airplane. In given situation it is reasonable that cat and dog classes are perceived as similar compared to other classes. Learned representation for both ReNet and ReNet with modification are not linearly separable. There are some fragments of representation where one of classes is dominant, but all labels are mixed up. This may be reason why classification task is difficult for ReNet networks.

Assuming that the loss landscape visualization plots are representative one may assume, that ReNet networks have obtained minimum. This minimum can be global or local. If it is global, then ReNet networks are not able of achieving loss values as low as ones obtained for convolutional networks. However results discussed in \cite{Goodfellow-et-al-2016} provide, that deep networks rarely obtain global minimum. Most of the times achived minimum is local, but the value of loss is sufficiently low. One of possibilities is that ReNet networks require some special optimization techniques.
